\cvsection{\textbf{WORK EXPERIENCE}}
\begin{cventries}

  \cventry
  {\href{https://healthplix.com/}{HealthPlix Technologies }}
  {Frontend - Engineer}
  {Bengaluru}
  {July'22 - Present}
  {
    \begin{cvitems}
    \item \textbf{Integrated AI-powered documentation} using OpenAI APIs, enabling doctors to record conversations and upload documents for automated structured summaries in IPD and OPD workflows.
    % \item Resolved \textbf{200+ production tickets} including \textbf{22 P0/P1 critical hotfixes}, implementing \textbf{Sentry integration} with custom sampling for proactive observability and real-time error monitoring across user journeys.
    \item Build functionality for IPD and OPD, contributing to over \textbf{₹5 Crore} in revenue by improving efficiency in doctor-patient workflows.
    \item Architected \textbf{TypeScript migration} and \textbf{Zustand state management} implementation, reducing code duplication by unifying Patient Popup component across OPD and Lab modules, improving maintainability and reducing re-rendering overhead by \textbf{25\%}.
    \item Built and maintained reusable UI library migrating from legacy patterns to modern \textbf{Shadcn/Tailwind architecture}, improving frontend consistency, accelerating cross-team development, and incorporating best practices from internal Brownbag sessions.
    \item Identified and resolved \textbf{90\% of revenue leakage cases} from outperforming ads and stabilized IPD/OPD billing systems by fixing high-stakes regressions in deposit calculations and payment-split logic, directly protecting revenue integrity.
    \item Led front-end delivery of \textbf{HALO AI Summarization module} using \textbf{Server-Sent Events (SSE)} for real-time data streaming, managing complex state synchronization and live parsing for AI-powered medical dictation workflows.
    \item Contributed to architectural improvements including \textbf{Watermelon DB offline storage} for rural connectivity, \textbf{Amplitude analytics integration}, and mentored team members on TypeScript migration, state management patterns, and feature architecture.
\end{cvitems}

  }

  \cventry
  {\href{https://www.aramex.com/in/en}{Aramex India Pvt Ltd}}
  {Data Science Intern}
  {Mumbai}
  {Aug'21 - Jan'22}
  {
    \begin{cvitems}
    \item Improved last-mile performance in Bahrain by improving address information extraction logic.
    \item Developed and trained a model to map the addresses of the delivery points in Bahrain using block numbers and road numbers that \textbf{ increased the precision} of the trained model from \textbf{90\%} to \textbf{99\%}.
    \item Data analysis, pre-processing, and feature engineering was performed for reliable results.
    \item \textbf{Demonstrated exceptional performance} and contributions, leading to an \textbf{offer for a full-time role} with \textbf{Aramex India Pvt Ltd}.
    \end{cvitems}
  }

\end{cventries}
\vspace{-2mm}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: xetex
%%% TeX-master: "../cv.tex"
%%% End:
