\cvsection{\textbf{SELECTED PROJECTS}}
\begin{cventries}

  \cventry
  {}
  {\href{https://f20180039.github.io/anshuman-singh/}{Portfolio Website}}
  {}
  {2026}
  {
    \begin{cvitems}
      \item Personal portfolio for frontend work, projects, and professional profile; also used as the resume-name redirect.
    \end{cvitems}
  }

  \cventry
  {}
  {\href{https://exploding-production.onrender.com}{Exploding Production Game}}
  {}
  {2026}
  {
    \begin{cvitems}
      \item Codex-assisted browser game deployed on Render with interactive gameplay, polished UI flow, and production-hosted routing.
    \end{cvitems}
  }

  \cventry
  {}
  {\href{https://multiplayer-frontend-x0cb.onrender.com}{Multiplayer Game Hub}}
  {}
  {2026}
  {
    \begin{cvitems}
      \item Multiplayer game platform with multiple browser games, shared entry flow, and frontend interactions designed for real-time play sessions.
    \end{cvitems}
  }

  \cventry
  {}
  {Snapgram - \href{https://stalkergram.netlify.app}{Live Demo} | \href{https://github.com/f20180039/snapgram}{GitHub}}
  {}
  {Mar'24 - Apr'24}
  {
    \begin{cvitems}
      \item Full-stack Instagram clone with authentication, posts, likes, comments, real-time updates, React, Firebase, and Tailwind CSS.
    \end{cvitems}
  }

  \cventry
  {HealthPlix Technologies}
  {Inpatient Department (IPD) Module Development}
  {}
  {July'22 - Present}
  {
    \begin{cvitems}
      \item Developed IPD workflows for patient management in larger hospitals and integrated AI-assisted input for VisitPad notes.
    \end{cvitems}
  }

  \cventry
  {HealthPlix Technologies}
  {Flagship Electronic Medical Record (EMR) Product Enhancements}
  {}
  {July'22 - Present}
  {
    \begin{cvitems}
      \item Revamped consultation, patient history, and medication views for healthcare providers, supporting over \textbf{INR 5 Crore} in OPD sales.
    \end{cvitems}
  }

  \cventry
  {Mentor: Prof. Kamlesh Tiwari}
  {One Shot Fingerprint Singular-Point Detector}
  {}
  {Mar'22 - May'22}
  {}

  \cventry
  {Mentor: Prof. Kamlesh Tiwari}
  {Architecture Image Matching}
  {}
  {Mar'22 - May'22}
  {}

  % \cventry{Mentor: Prof. Dr. Sujan Yenuganti}
  % {Laser Applications in Biomedical Field}
  % {}
  % {Mar'21 - Apr'21}
  % {}

  % \cventry{Mentor: Prof. Puneet Mishra}
  % {Design and Analysis of Temperature Control System using Conventional PI and Advanced ANN Controllers}
  % {}
  % {Jan'21 - July'21}
  % {}

  \cventry{Mentor: Prof. Surekha Bhanot}
  {A Closer Look at Spatiotemporal Convolutions for Action Recognition}
  {}
  {Mar'20 - May'20}
  {}

\end{cventries}
\vspace{-2mm}
